---
title: "Lab6"
author: "Andrea Bruzzone, Thomas Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Package Info
The Knapsack package contains three different function to solve the knapsack problem. 
In the Knapsack problem we have a knapsack with a limited weight W and a  number of items i, each with a weight $w_{i}$ and a value $v_{i}$. The goal of the problem is to fill the knapsack with the items so that the total weight is less than or equal to W and the total value is as large as possible. 

The three functions take as input a Data frame with variables v and w, which have to be positive values.

## Brute force search 
This function solves the Knapsack probem by brute force.

For example:
```{r}
#brute_force_knapsack(data.frame(w=c(29,11,4,50,33,9,20,6 ),v=c(2,7,11,2,9,33,6,45 )),W =20)
```


```{r, echo = FALSE}
#Sys.time()
#brute_force_knapsack(data.frame(w=c(29,11,4,50,33,9,20,6 ),v=c(2,7,11,2,9,33,6,45 )),W =20)
#Sys.time()
```

## Dynamic programming 
This function solves the 0/1 Knapsack problem using dynamic programming.
```{r}

```

## Greedy heuristic
This function solves the Knapsack problem using a greedy heuristic approach. It does not return an exact result but is computationally faster than the other approaches in this package. 

```{r}

```


## Profiling



```{r, echo=FALSE}

```

## Parallelize Brute force search 
We added an argument, `parallel`, in the brute force function that when it is set to TRUE the function parallelize over the multiple cores. We used a computer with 8 cores.

```{r, echo=FALSE}

```