---
title: "Lab6"
author: "Andrea Bruzzone, Thomas Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Package Info
The Knapsack package contains three different function to solve the knapsack problem. 
In the Knapsack problem we have a knapsack with a limited weight W and a  number of items i, each with a weight $w_{i}$ and a value $v_{i}$. The goal of the problem is to fill the knapsack with the items so that the total weight is less than or equal to W and the total value is as large as possible. 

The three functions take as input a Data frame with variables v and w, which have to be positive values.

## Brute force search 
This function solves the Knapsack probem by brute force.

For example. for n = 16 objects:
```{r, echo = FALSE, message = FALSE}
library(Lab6)
```

```{r}

#system.time(brute_force_knapsack(knapsack_generator()[1:16,],W =2000))

```

The brute force function takes around 27 seconds to run the algorithm for n = 16 objects.


## Dynamic programming 
This function solves the 0/1 Knapsack problem using dynamic programming.

For example, for n = 500 objects: 
```{r}
#system.time(knapsack_dynamic(knapsack_generator()[1:500,],W =2000))
```

The dynamic function takes around 38 seconds to run the algorithm for n = 500 objects.


## Greedy heuristic
This function solves the Knapsack problem using a greedy heuristic approach. It does not return an exact result but is computationally faster than the other approaches in this package. 

For example, for n = 1000000 objects: 
```{r}
#system.time(greedy_knapsack(knapsack_generator()[1:1000000,],W =2000))
```

The greedy heuristic function takes around 50 seconds to run the algorithm for n = 1000000 objects.


## Profiling
We try to improve this appaling performance. Using the Rprof we discovered that the problem is the use of the data frame, in fact replacing the data frame with matrix the functions are faster.

```{r}

```


## Parallelize Brute force search 
We added an argument, `parallel`, in the brute force function that when it is set to TRUE the function parallelize over the multiple cores. We used a computer with 8 cores.

```{r}
#system.time(brute_force_knapsack(knapsack_generator()[1:16,],W =2000), parallel = TRUE)
```